The imprint of global magma oceans on exoplanet demographics

### 2022-10-26 src/tex/ms.tex
add description of null and alternative hypothesis and corresponding figure

\subsubsection{Definition of the magma ocean hypothesis and null hypothesis}
\todo{Define the null and alternative hypotheses}
...

>>>>

\subsubsection{Definition of the magma ocean hypothesis and null hypothesis}
\todo{Define the null and alternative hypotheses}
\begin{note}
    As a null hypothesis, we consider the case where the planetary radius distribution is independent of the instellation,
    \begin{equation}
        h_{\mathrm{null}}(\theta, S) = \theta,
    \end{equation}
    where $\theta$ is the set of parameters defining the radius distribution.
    We further define an alternative hypothesis that describes radius changes due to steam atmospheres and water in the melt.
    As motivated above, this hypothesis takes the form of a step function in instellation $S$, where the step occurs at the outer edge of the runaway greenhouse region.
    Our main observable shall be the average planet radius in the planet population inside and outside this threshold.
    The magma ocean hypothesis is then defined as
\begin{equation}
    h_{\mathrm{MO}}(\theta, S) =
%        \begin{cases}
%        1 & \text{if } x \in \mathbb{Q}\\
%        0 & \text{if } x \in \mathbb{R}\setminus\mathbb{Q}
%    \end{cases}
        \begin{cases}
        h_{\mathrm{null}} & \text{for } S \leq S_\mathrm{thresh}\\
        <R_\mathrm{P}> (f_\mathrm{steam}, f_\mathrm{water}) & \text{for } S > S_\mathrm{thresh}.
    \end{cases}
\end{equation}
    Here, $f_\mathrm{steam}$ and $f_\mathrm{water}$ are predictions from the steam atmosphere and water incorporation models, respectively.
    They are assumed to act additively on the planet radii and thus on their average $<R_\mathrm{P}>$.

%        \begin{cases}
%        \end{cases}

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/HnullHmo.pdf}
        \caption{Average radius predictions of the null hypothesis and magma ocean hypothesis. The sharp boundary of the runaway greenhouse regime causes a discontinuity at the threshold instellation $S_\mathrm{thresh}$, which we set to \SI{280}{\watt\per\meter\squared} in the fiducial case.}
        \label{fig:HnullHmo}
    \end{centering}
\end{figure}
    Figure~\ref{fig:HnullHmo} shows the null and alternative hypotheses as a function of instellation.
    The value for the average radius \textit{outside} the runaway greenhouse regime was computed from our nominal observed sample, whereas the radius change in the magma ocean case compared to the null hypothesis is a prediction from the magma ocean model, evaluated on the same sample.

\end{note}
...
